Quality Definitions of Qualities

### 2019-10-08 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
added installability and correctness

A measure of the ease of installation.

@@

Software is correct if it matches its specification.  There is no direct tool or
method for measuring correctness. One way of building confidence in correctness
is by reviewing to ensure that each requirement stated is one that the
stakeholders and experts desire.  By maintaining traceability, consistency and
unambiguity, we can reduce the occurrence of errors and make the goal of
reviewing for correctness easier.

>>>>

A measure of the ease of installation.\\
Installability is related to the effort required to install a software in a specified environment. In other words, its capability to be installed in a specified environment.

@@

Software is correct if it matches its specification.  There is no direct tool or
method for measuring correctness. One way of building confidence in correctness
is by reviewing to ensure that each requirement stated is one that the
stakeholders and experts desire.  By maintaining traceability, consistency and
unambiguity, we can reduce the occurrence of errors and make the goal of
reviewing for correctness easier.\\
 The extent to which a software's specification, design and implementation is free from errors is its correctness. The quality of a software's operation is dependent on the degree of correctness. Correctness and reliability are said to have dependencies, such that if a system exhibits a high degree of correctness then it tends to be reliable.
